Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-06 doc/JFLA2022/Slides/Slides.tex
small changes to JFLA slides
micro-modifs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{The \Hydras project}
  \begin{block}{}
    \begin{itemize}
   \item Experimental platform for the  development of \textcolor{lookcolor}{maintained} and \textcolor{lookcolor}{documented} libraries of formal proofs.
    \item A project of \community, developped on GitHub
      \begin{itemize}
      \item CI/CD
        \item Tools for collaboration (issues, PR, etc.)
        \end{itemize}
           \item A book in PDF (300p), generated  with \textcolor{lookcolor}{\alectr} and \LaTeX, continuously updated and deployed
    \end{itemize}
  \end{block}
  \begin{block}{Contents}
    \begin{itemize}
    \item Evolved version  of two contributions: \textcolor{plugincolor}{Cantor} and \textcolor{plugincolor}{Additions}
    \item Maintenance of \textcolor{plugincolor}{Ackermann}
      (part of Russel O'Connor's \textcolor{plugincolor}{Goedel})
    \item Bridge to \textcolor{plugincolor}{Gaia} (José Grimm) (\emph{in construction})

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{}
    \Hydras presents a consistent set of examples, which allows us to formalize
    some \textcolor{mathcolor}{discrete math}, discuss
    \textcolor{coqstylecolor}{\coq style, specification and proof patterns}, and depend on \textcolor{plugincolor}{a few plug-ins}.
  \end{block}
  \begin{block}{}
    \begin{description}
    \item[hydra battles:]

@@

\begin{scope}[xshift=-5.7cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel\footnote{R. O'Connor} };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=2.2cm] (pock) { Pocklington\footnote{O. Caprotti \& M. Oostdijk}};
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (cantor) { Cantor\footnote{C. \& E. Contejean}};

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles.}

@@

\begin{frame}
  \frametitle{Conclusion and perspectives}
  \begin{block}{}
    \begin{itemize}
    \item \Hydras wants to provide  a connection between scientific litterature and proof assistant technology:
      \begin{itemize}
      \item For the mathematician, it gives a concrete view of the mathematical contents: full proofs, examples, computable functions whenever possible, etc.
        \item  For the \coq learner, it provides a consistent set of examples,
          allowing to present and compare various formalization and proving techniques.
          \item It allows the development team to experiment various techniques of CI/CD and project organization and maintenance.
      \end{itemize}
    \end{itemize}
  \end{block}
  \end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{The \Hydras project}
  \begin{block}{}
    \begin{itemize}
   \item Experimental platform for the  development of \textcolor{lookcolor}{maintained} and \textcolor{lookcolor}{documented} libraries of formal proofs.
    \item A project of \community, developped on GitHub
      \begin{itemize}
      \item CI/CD
        \item Tools for collaboration (issues, PR, etc.)
        \end{itemize}
      \item A book in PDF (300p), generated  with \textcolor{lookcolor}{\alectr} and \LaTeX, continuously updated and deployed
  \item          When appropriate, we present various proofs of the same statement, and interesting false starts.
    \end{itemize}
  \end{block}
  \begin{block}{Contents}
    \begin{itemize}
    \item Evolved version  of two contributions: \textcolor{plugincolor}{Cantor} and \textcolor{plugincolor}{Additions}
    \item Maintenance of \textcolor{plugincolor}{Ackermann}
      (part of Russel O'Connor's \textcolor{plugincolor}{Goedel})
    \item Bridge to \textcolor{plugincolor}{Gaia} (José Grimm) (\emph{in construction})

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{}

 \Hydras presents a consistent set of examples, which allows us to formalize
    some \textcolor{mathcolor}{discrete math}, discuss
    \textcolor{coqstylecolor}{\coq style, specification and proof patterns}.

    %, and depend on \textcolor{plugincolor}{a few plug-ins}.

  \end{block}
  \begin{block}{}
    \begin{description}
    \item[hydra battles:]

@@

\begin{scope}[xshift=-5.7cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel\footnote{R. O'Connor} };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=2.2cm] (pock) { Pocklington\footnote{O. Caprotti \& M. Oostdijk}};
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (cantor) { Cantor\footnote{C. \& E. Contejean
    \textcolor{pauillac}{(Pauillac 2006)}}};

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles
  (extends \textcolor{banyuls}{Banyuls 2018}).}

@@

\begin{frame}
  \frametitle{Conclusion and perspectives}
  \begin{block}{}
    \begin{itemize}
    \item \Hydras wants to provide  a connection between scientific litterature and proof assistant technology:
      \begin{itemize}
      \item For the mathematician, it gives a concrete view of the mathematical contents: full proofs, examples, computable functions whenever possible, etc.
        \item  For the \coq learner, it provides a consistent set of examples,
          allowing to present and compare various formalization and proving techniques.
          \item It allows the developers of the project to experiment various techniques of CI/CD and project organization and maintenance.
      \end{itemize}
    \end{itemize}
  \end{block}
  \end{frame}
